Fréchet Distance

### 2022-12-26 docs/paper.tex
display correct diagram grid in free space plots

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/polygonal_curves.pdf}
        \input{images/frechet_distance/polygonal_curves.tex}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/free_space_polygonal_curves.pdf}
        \input{images/frechet_distance/free_space_polygonal_curves.tex}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ from \autoref{fig_complex_free_space_lines_example} 
    and distance $\varepsilon = 0.73$ using euclidean distance. (Figure inspired by \cite{buchin_four_2017})}
  \label{fig_complex_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \resizebox{0.5\textwidth}{!}{
    \input{images/frechet_distance/free_space_monotone_curve.tex}
  }
  \caption{A monotonically increasing curve (red) through the free space diagram. 
    (Figure inspired by \cite{buchin_four_2017})}
  \label{fig_free_space_curve}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/polygonal_curves.pdf}
        \input{images/frechet_distance/polygonal_curves.tex}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/free_space_polygonal_curves.pdf}
        % \input{images/frechet_distance/free_space_polygonal_curves.tex}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ from \autoref{fig_complex_free_space_lines_example} 
    and distance $\varepsilon = 0.73$ using euclidean distance. (Figure inspired by \cite{buchin_four_2017})}
  \label{fig_complex_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \resizebox{0.5\textwidth}{!}{
    \includegraphics[width=\textwidth]{images/frechet_distance/free_space_monotone_curve.pdf}
    % \input{images/frechet_distance/free_space_monotone_curve.tex}
  }
  \caption{A monotonically increasing curve (red) through the free space diagram. 
    (Figure inspired by \cite{buchin_four_2017})}
  \label{fig_free_space_curve}
\end{figure}
